---
title: "Testing"
author: "Kadee_N_Lawrence"
date: "`r Sys.Date()`"
output: html_document
---
<body style="background-color:tan;">

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(datasets)
library(ggplot2)

```

## Rmarkdown Notes {.tabset}

### Help
Here are two links to webpages that should help with additional questions.  

NOTE that we are working with an HTML document.  

- [Link1](https://bookdown.org/yihui/rmarkdown-cookbook/html-output.html)  
- [Link2](https://appsilon.com/r-markdown-tips/#:~:text=To%20insert%20an%20image%2C%20you,looks%20smaller%20by%20default%20though.)  

### Dataset
```{r CodeIrisData, include = TRUE}
#Create a csv of data set "iris" and then upload it
write.csv(x = iris,"iris_dataset.csv",quote=F)
dataset <- read.csv("iris_dataset.csv", header = TRUE)

#Table of just the species setosa 
setosa <- dataset %>% filter(Species=="setosa")
```

### Setosa Table
```{r tableSetosa, include = TRUE}
#Create a simple table aligning the columns "left", "center", "center", "right", "right", and with the caption "Table1:..."
knitr::kable(setosa, "simple", align = "lccrr", caption = "Table1: Setosa sepal length, sepal width, petal length, and petal width")
```

### Setosa Plots
```{r plotSetosaSepal, fig.cap="Figure1_a: Setosa sepal length vs sepal width"}
#Make simple plot for setosa sepal length vs sepal width
plot(setosa$Sepal.Length, setosa$Sepal.Width, pch = 15, col="pink")
```
</br>

```{r plotSetosaPetal, fig.cap="Figure1_b: Setosa petal length vs petal width"}
#Make simple plot for setosa petal length vs petal width
plot(setosa$Petal.Length, setosa$Petal.Width,, pch = 15, col="pink")
```

```{r plotSetosaFiguresTogether, fig.cap="Figure1: a)Setosa sepal length vs sepal width. b)Setosa petal length vs petal width"}
par(mfrow=c(1,2))
plot(setosa$Sepal.Length, setosa$Sepal.Width, pch = 15, col="pink", xlab="sepal length", ylab="sepal width", main = "a")
plot(setosa$Petal.Length, setosa$Petal.Width,, pch = 15, col="pink", xlab="petal length", ylab="petal width", main = "b")
```

### Iris Dataset Plots
```{r plotIrisPetalLen, fig.cap="Figure2: Petal Length of all Species in Iris Dataset"}

#Create species list to set for x scale later
species_list = c("setosa", "versicolor", "virginica")

#Now lets plot the petal length of each species with the mean 
Figure2 <- ggplot(dataset, aes(Species, Petal.Length, fill=Species)) + geom_point(show.legend = FALSE, size = 4, pch=21, stroke = 1) + stat_summary(geom = "point", fun = "mean", size = 4, shape = 24, fill = "black") + theme_bw() + scale_fill_manual(name="Species Color", values = c("pink", "violet", "lightblue")) + scale_x_discrete(limits = species_list) + ylab("Petal Length") + xlab("Species") + ggtitle("Iris Petal Lengths by Species")

print(Figure2)
```

### How do I save my plots?
**The simple way**

This is the simplest way to save the figure as a pdf using ggsave. You can change the file format by changing the .pdf to .eps, .png, or whatever format you're wanting. 

```
ggsave("IrisPetalLengthsSpecies.pdf", Figure2, width=10, height=10)
```


**The more complex way**

For this method you will create a function that will then save your figure. This function was created by Madison Y. and allows you to specify what type of file you want to save the figure as and the size. 

NOTE: this function saves the figure in three different file formats: .pdf, .eps, and .png

```
install.packages("ggplot2")
install.packages("stringr")
###HAD to Return to terminal and do -sudo apt install cmake
install.packages("ggpubr", repos = "https://cloud.r-project.org/", dependencies = TRUE)

library(ggplot2)
library(stringr)
library(ggpubr)

##Function to export plot by Madison Y.
ExportPlot <- function(gplot, filename, width=2, height=1.5) {
  # Export plot in PDF and EPS.
  # Notice that A4: width=11.69, height=8.27
  ggsave(paste(filename, '.pdf', sep=""), gplot, width = width, height = height)
  postscript(file = paste(filename, '.eps', sep=""), width = width, height = height, family = "sans")
  print(gplot)
  dev.off()
  png(file = paste(filename, '_.png', sep=""), width = width * 100, height = height * 100)
  print(gplot)
  dev.off()
}
```
How to call the function:
```
ExportPlot(Figure2,"IrisPetalLengthSpecies",width=10,height=6)
```
### How to pivot a dataset
How to pivot a dataframe.
```{r DataFrame}
#Let's make a dataframe
Data <- data.frame(R_23 = c(1,2,3,4,5), R_24 = c(6,5,8,3,9), R_25 = c(7,3,0,3,2))
rownames(Data) <- c("Row1", "Row2", "Row3", "Row4", "Row5")
```

```{r DataTable, include = TRUE, echo = FALSE}
#Create a simple table aligning the columns "right", "right", "right", and with the caption "Table2.1:..."
knitr::kable(Data, "simple", align = "rrr", caption = "Table2.1: Data")
```

```{R pivotDataFrame}
#We can use a function t() from tidyr to pivot our dataset
DataPivoted <- Data |> t()
```

```{r pivotDataTable, include = TRUE, echo = FALSE}
#Create a simple table aligning the columns "right", "right", "right", "right", "right", and with the caption "Table2.2:..."
knitr::kable(DataPivoted, "simple", align = "rrrrr", caption = "Table2.2: DataPivoted")
```